---
title: "A Homework of Biblical Proportions"
author: "Meiyuan Li"
---

In this HW, we will analyze the text of the bible. The ascii version resides in the file "ascii_bible.txt" on Camino. Use an editor to familiarize yourself with the structure of the file. Then perform the following operations, listed below as questions for you to answer. 

## Q1: Read in the file using any R function you like and store each verse in a text array. After which print the top 20 verses. (Remove the top two lines which contain the title.)

```{r}
library(stringr)
text = readLines("/Users/Meiyuan/Downloads/3490 R/DATA/ascii_bible copy.txt")
text = str_replace_all(text,"\t"," ")
text = gsub("Book \\d\\d\\s.*","",text)
text = str_replace_all(text,"        ","")
idx = which(nchar(text)==0)
size = length(text)
text = text[setdiff(seq(1,size),idx)]
#add an identifier "XYZ" for later subsitution
text = paste(text, collapse = "XYZ")
text = str_replace_all(text,"XYZ0","     0")
text = str_replace_all(text,"XYZ1","     1")
text = str_replace_all(text,"XYZ"," ")
final = strsplit(text,"     ", perl = TRUE)
verse = unlist(final)
#write out the verse for later use
#write(verse, file = "verse.txt")
```


## Q2: How many verses are there in total? 
```{r}
length(verse)
```


## Q3: Each verse has the number "CCC:VVV" where CCC is the chapter number and VVV is the verse number. How many chapters are there? 

```{r}
verse = readLines("/Users/Meiyuan/verse.txt")
verse = as.vector(verse)
count = 0
for (j in 1:length(verse)) {
  if(!identical(substring(verse[j],1,3),substring(verse[j+1],1,3)) || (substring(verse[j],1,7) == "001:001" && identical(substring(verse[j-1],1,3),substring(verse[j+1],1,3)) )){
      count = count + 1
  }
    
}
count
```

## Q4: Extract an array for the verse numbers, and also one for the verse text.
```{r}
verseNumber = substring(verse,1,7)
verseText = substring(verse,9)
```
## Q5: Lower case all text.

```{r}
lowerText = tolower(verseText)
```

## Q6: Convert the text of all verses into a Corpus using the **tm** package. 
```{r}
library(tm)
library(NLP)
verseTm = Corpus(VectorSource(lowerText))
```

## Q7: Remove all punctuation. Use a corpus function for this. How many unique words are there in the bible? 

```{r}
library(tm)
noPunc = tm_map(verseTm,removePunctuation)
verseTDM = TermDocumentMatrix(noPunc,control=list(minWordLength=1))
inspect(verseTDM)
```


## Q8: Remove all stopwords. Now how many unique terms are there? 

```{r}
noStopwords = tm_map(noPunc,removeWords,stopwords("english"))
verseTDM2 = TermDocumentMatrix(noStopwords,control=list(minWordLength=1))
inspect(verseTDM2)
```


## Q9: Now stem the text, to remove multiplicity of similar words of the same root. 

```{r}
noStemwords = tm_map(noStopwords, stemDocument)
```


## Q10: How many distinct words are there in the bible, after stemming?

```{r}
verseTDM3 = TermDocumentMatrix(noStemwords,control=list(minWordLength=1))
inspect(verseTDM3)
```


## Q11: Convert the TDM into a matrix and find the 50 most common words in the bible. 

```{r}
tdmMatrix = as.matrix(verseTDM3)
rowSums = rowSums(tdmMatrix)
wordCount = sort(rowSums, decreasing = TRUE)
top50 = head(wordCount, n=50)
top50
```

## Q12: Make a wordcloud of the top 100 words in the bible. 
```{r}
library(wordcloud)
top100 = head(wordCount, n=100)
tdmNames = names(top100)
wordcloud(tdmNames,top100)
```


## Q13: Mood score the original text of the bible (before stemming)

```{r}
library(tm)
poswords = unlist(read.csv("/Users/Meiyuan/Downloads/pos.csv"))
negwords = unlist(read.csv("/Users/Meiyuan/Downloads/neg.csv"))

fullverse = paste((unlist(noStopwords)),collapse = " ")
allwords = str_split(fullverse,"\\s+")
posmatch = match(unlist(allwords),poswords)
numposmatch = length(posmatch[which(posmatch>0)])
negmatch = match(unlist(allwords),negwords)
numnegmatch = length(negmatch[which(negmatch>0)])
print(c(numposmatch,numnegmatch))

```


